\section*{Ethics Approval and Informed Consent}

This study used only publicly available, de-identified genome-wide association study and expression quantitative trait locus summary statistics. No new individual-level data were generated or accessed, and no new ethical approval or informed consent was required. The original data sources, including GTEx, FinnGen, OpenGWAS, and the eQTL Catalogue, obtained ethics approvals and participant consent within their respective consortia.

\section*{Consent for Publication}

Not applicable. This study used only de-identified summary-level data and contains no individual patient information, images, or recordings.

\section*{Data Availability}

Public summary statistics analyzed in this study are available from the \href{https://gtexportal.org/home/}{GTEx Portal}, \href{https://r13.finngen.fi/}{FinnGen release R13}, \href{https://gwas.mrcieu.ac.uk/}{OpenGWAS}, and the \href{https://www.ebi.ac.uk/eqtl/}{eQTL Catalogue} datasets QTD000316, QTD000311, and QTD000356. The corrected analysis scripts, the 68-row primary result table with exposure and outcome association fields, the relaxed-threshold results, reproducibility-audit outputs, and curated validation tables are deposited in a versioned public archive at \href{https://github.com/muhaoyang0616/skin_drug_target_mr/releases/tag/v1.0.0}{GitHub release v1.0.0} (archived on Zenodo at \href{https://doi.org/10.5281/zenodo.21331678}{10.5281/zenodo.21331678}). Source code is released under the MIT License, and manuscript source, figures, documentation, and machine-readable result tables are released under the Creative Commons Attribution 4.0 International License; raw GTEx and FinnGen files are not redistributed and remain subject to the terms of their originating resources.

\section*{Funding}

This work received no specific grant from any funding agency in the public, commercial, or not-for-profit sectors; therefore, no funder had any role in study design, analysis, interpretation, manuscript preparation, or the decision to submit.

\section*{Competing Interests}

The authors declare that they have no competing financial or non-financial interests related to the content of this article.

\section*{Authors' Contributions}

MH conceived and designed the study, performed the data analysis, interpreted the results, and drafted the manuscript. JS supervised the study, contributed to data interpretation, and critically revised the manuscript. Both authors read and approved the final version and agree to be accountable for the content of this work.

\section*{Acknowledgments}

The authors acknowledge the GTEx Consortium, FinnGen project, OpenGWAS database, and eQTL Catalogue for making their summary statistics publicly available. We thank the participants and investigators of these consortia for their contributions to open science.

\section*{AI-Assisted Technologies Disclosure}

OpenAI Codex was used solely for language editing, cross-document consistency checking, and formatting. It was not used to generate or alter research data, statistical analyses or results, or scientific conclusions. All AI-assisted edits were reviewed and approved by the authors, who take full responsibility for the final manuscript.
